Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-26 paper.tex
Add the 3-tier data marketplace description to related work

By solving the inefficiencies of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry or Web 3.0 based on the revolutionary distributed ledger technology, the \textbf{Tangle}. It is a secure, scalable and feeless transaction settlement layer which enables micropayments transaction. On top of that, Masked Authenticated Messaging(MAM)\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public. On the basis of the Tangle and MAM, IOTA foundation proposed a fully decentralized Data MarketPlace which is suitable for IoT streaming data that not only allow data owners and consumers to trade on Tangle but also protect privacy and assure data integrity from source with MAM. But only the data buyout doesn't meet the need of the real world, such as data subscription and a specific time period of data maybe needed for different uses. Moreover, even though IOTA needs less computing power than other blockchain system, doing PoW and unstable network environment are still the bottleneck for low-level devices, it may take 2 or more minutes to issue a transaction to Tangle under MAM protocol.

Our proposed framework is developed based on IOTA Data Marketplace. We aim to solve the efficiency and reliability issue for low-level devices in blockchain system and to make the buying and selling process closer to real world that meet actual needs and usages.

>>>>

By solving the inefficiencies of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry or Web 3.0 based on the revolutionary distributed ledger technology, the \textbf{Tangle}. It is a secure, scalable and feeless transaction settlement layer which enables micropayments transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public. On the basis of the Tangle and MAM, IOTA foundation proposed a fully decentralized Data MarketPlace which is suitable for IoT streaming data that not only allow data owners and consumers to trade on Tangle but also protect privacy and assure data integrity from source with MAM. But only the data buyout doesn't meet the need of the real world, such as data subscription and a specific time period of data maybe needed for different uses. Moreover, even though IOTA needs less computing power than other blockchain system, doing PoW and unstable network environment are still the bottleneck for low-level devices, it may take 2 or more minutes to issue a transaction to Tangle under MAM protocol.

A different framework design proposed by Pooja Gupta, Salil S.Kanhere and Raja Jurdak\cite{3tierDataMarket} could solve the efficiency problem as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with smart contract which consists of provider, consumer and broker. Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers. However, there are some potential threats need to be resolved, such as payment fairness, authentication of the participants, faithful delivery of data and probable malicious behaviour of data marketplace participants.

Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture that put data stream and trading process on distrubted ledgers. In our infrastructure, the identity of each participants could be easily verified with a self-soverign identity system, also we design the refunding mechanism to protect the payment fairness. Moreover, with MAM as our data storage on IOTA, data could be delivered securely and faithfully without any third-parties.
